Implications of afforestation policies for global markets

### 2023-06-24 paper.Rmd
Update paper.Rmd

A transition from deforestation to reforestation, in general, induce the displacement of land use abroad despite the uncertain roles of international trade due to the heterogeneity of regions/countries (Meyfroidt, Rudel and Lambin, 2010; Lambin and Meyfroidt, 2011). DeFries et al. (2010) found a strong correlation between forest loss and exports of agricultural products. On the other hand, Turner et al. (2005) investigated the role of trade on forests in the context of the Free Trade Area of the Americas (FTAA) using the spatial partial-equilibrium Global Forest Products Model and found that FTAA has a positive impact on forest resources.

>>>>

A transition from deforestation to reforestation, in general, induces the displacement of land use abroad despite the uncertain roles of international trade due to the heterogeneity of regions/countries [@meyfroidt2010] [@lambin2011] DeFries et al. [@defries2010] found a strong correlation between forest loss and exports of agricultural products. On the other hand, Turner et al. [@turner2005] investigated the role of trade on forests in the context of the Free Trade Area of the Americas (FTAA) using the spatial partial-equilibrium Global Forest Products Model and found that FTAA has a positive impact on forest resources.
